\documentclass[10pt]{article}


\setlength{\oddsidemargin}{0in}
\setlength{\textwidth}{6.5in}

\setlength{\topmargin}{-0.25in}
\setlength{\textheight}{10.5in}

% Heading
\begin{document}
% Title

\begin{center}
\Large \textbf{Summer Plan Items for GUI group} \normalsize
\end{center}

\vspace{.5in}

\Large \textbf{Major Items} \normalsize
\begin{enumerate}

\item Boxes [jhhwang, mhatoun, rly]
\begin{enumerate}
\item Develop a way of specifying any predicate for all of the operators. [6/28]
\item Finish the properties dialog for all of the boxes. [7/12]
\item Save and load the operators and their predicates to the database. [7/26]
\end{enumerate}

\item Superboxes [rly]
\begin{enumerate}
\item Composition and decomposition of superboxes. [6/14]
\item Design of the sleepycat database tables with superboxes and extensions (such as security, users, etc) in mind. [6/28]
\item Saving and loading the superboxes as nodes to the sleepycat database. [7/12]
\item Saving and loading all of the primitive boxes separately into the superboxes as they're being opened. [7/19]
\item Implementing hierarchical tree representation of superboxes in the hierarchy tabbed pane [7/26]
\end{enumerate}

\item Monitoring [arsinger]
\begin{enumerate}
\item Supporting the workflow generator and updating type/aggregate stream
system [7/1]
\item Communication with workflow generator through sleepycat? tcp/ip? [7/10]
\item Communication with scheduler using sleepycat [7/14]
\item performance numbers, output, delay, \% tuples passed, other information
stored using arc colors, tooltips, arc girth, etc. [7/17]
\item Supporting quality of service [7/26]
\end{enumerate}

\item Ad-hoc Queries [?]

\end{enumerate}

\vspace{.5in}

\Large \textbf{Other Items} \normalsize
\begin{enumerate}
\item Preparing ant and jikes for development under linux [rly] [6/21]
\item Migrate development tools to /pro/aurora [rly]
\item Documenting code and tool usage [rly]
\item Implementing superboxes as palette and storing it into the database
\item Converting java application into an applet
\item Aesthetics -- L\&F, logo...
\item Debugging, debugging, debugging!!
\item Set up bug tracking system
\end{enumerate}

\end{document}
